Lit Review Figure

### 2017-09-19 code/Lit_Review_Figure.Rmd
fixed colors for lit review figure

---
title: "Lit Review Figure"
output:
  pdf_document: default
  html_document: default
---

@@

Interactive plot

@@

```{r warning= FALSE, message =FALSE, out.width = "80%", echo=FALSE}
p1 = fig_data %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(days_cutoff = ifelse(days < 60, days, 120),
         task_group = factor(task_group, levels = task_group[order(task)])) %>%
  filter(task == 'task') %>%
ggplot(aes(y = var, x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type, alpha = days_cutoff))+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.5, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80"),
        legend.position = 'bottom') + 
  xlab("")+
  ylab("")

@@

mylegend<-g_legend(p1)

p3 <- grid.arrange(arrangeGrob(p1 + geom_point(color='#00BFC4')+theme(legend.position="none"),
                         p2 + theme(legend.position="none"),
                         nrow=1),
             mylegend, nrow=2,heights=c(10, 1))

@@

>>>>

---
title: "Lit Review Figure"
output:
  html_document: default
  pdf_document: default
---

@@

Interactive plot - not rendered for now

@@

```{r warning= FALSE, message =FALSE, echo=FALSE}
p1_legend = fig_data %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(days_cutoff = ifelse(days < 60, days, 120),
         task_group = factor(task_group, levels = task_group[order(task)])) %>%
  filter(task == 'task') %>%
ggplot(aes(y = var, x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type, alpha = days_cutoff))+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.5, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80"),
        legend.position = 'bottom') + 
  xlab("")+
  ylab("")

p1 = fig_data %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(days_cutoff = ifelse(days < 60, days, 120),
         task_group = factor(task_group, levels = task_group[order(task)])) %>%
  filter(task == 'task') %>%
ggplot(aes(y = var, x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type, alpha = days_cutoff), color='#00BFC4')+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.5, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80"),
        legend.position = 'bottom') + 
  xlab("")+
  ylab("")

@@

mylegend<-g_legend(p1_legend)

p3 <- arrangeGrob(arrangeGrob(p1 +theme(legend.position="none"),
                         p2 + theme(legend.position="none"),
                         nrow=1),
             mylegend, nrow=2,heights=c(10, 1))

@@

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('../output/Lit_Review_Plot.jpg')
```
